Paper 1

### 2018-09-09 paper1.tex
Proved Lemma 4

\begin{proof}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% First you have to complete the statement of the lemma.
	% This means that you have to replace both $\phi(a_n,b_n)$ and $\psi(a_n,b_n)$ with explicit formulae.
	% There is no need to show how you worked out what should replace $\phi$ and $\psi$, just enter the replacements into the statement of the lemma and then give the proof as if you always had always known what $\phi$ and $\psi$ are.
	% THE SYMBOLS $\phi$ AND $\psi$ SHOULD NOT APPEAR ANYWHERE IN THE STATEMENT OF THE LEMMA OR THE PROOF WHEN YOU SUBMIT.
	%
	% The proof is by induction.
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{proof}

>>>>

\begin{proof}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% First you have to complete the statement of the lemma.
	% This means that you have to replace both $\phi(a_n,b_n)$ and $\psi(a_n,b_n)$ with explicit formulae.
	% There is no need to show how you worked out what should replace $\phi$ and $\psi$, just enter the replacements into the statement of the lemma and then give the proof as if you always had always known what $\phi$ and $\psi$ are.
	% THE SYMBOLS $\phi$ AND $\psi$ SHOULD NOT APPEAR ANYWHERE IN THE STATEMENT OF THE LEMMA OR THE PROOF WHEN YOU SUBMIT.
	%
	% The proof is by induction.
	%
	First, we want to show that the sequence satisfies the first equation,
	$$\left(1+\sqrt{2}\right)^n = a_n + b_n \sqrt{2}.$$
	When $n=1$ the equations holds,
	\begin{align*}
		\mbox{LHS} = \left(1+\sqrt{2}\right)^1=1+\sqrt{2}\\	
		\mbox{RHS} = a_1+b_1\sqrt{2}=1+\sqrt{2}.
	\end{align*}
	So, $\mbox{LHS} = \mbox{RHS},$ and the equation holds for $n=1$.
	Assume the equations holds for a particular natural number $n$.
	Now, we want to show that the equation also holds for $n+1$.
	From our assumption we know,
	\begin{align*}
		\left(1+\sqrt{2}\right)^n &= a_n + b_n \sqrt{2}\\
		\left(1+\sqrt{2}\right)^n(1+\sqrt{2}) &= (a_n + b_n \sqrt{2})(1+\sqrt{2})\\
		\left(1+\sqrt{2}\right)^{n+1}&= a_n + a_n\sqrt{2} + b_n\sqrt{2} +2b_n\\
		\left(1+\sqrt{2}\right)^{n+1}&= (a_n+2b_n) + (a_n+b_n)\sqrt{2}\\
		\left(1+\sqrt{2}\right)^{n+1} &= (a_{n+1}) + (b_{n+1})\sqrt{2}
	\end{align*}
	Hence, the equation holds for $n+1$ when it holds for $n$. 
	By induction on $n$, the equation holds for all natural number $n$.

	Next, we will show that the following equation also holds for the described sequences:
	$$a_n^2-2b_n^2 = (-1)^n.$$
	When $n=1$,
	\begin{align*}
	\mbox{LHS} = a_1^2-2b_1^2=1-2=-1\\	
	\mbox{RHS} = (-1)^1=-1{2}.
	\end{align*}
	So $\mbox{LHS} = \mbox{RHS},$ and the equation holds for $n=1.$
	Now, assume that the equation holds for a particular natural number $n$.
	We want to show that the equation must also hold for $n+1$.
	Now, consider
	\begin{align*}
		a_{n+1}^2-2b_{n+1}^2 &= (a_n+2b_n)^2-2(b_n+a_n)^2\\
		&= a_n^2 + 4b_na_n +4b^2_n - 2(b_n^2+2a_nb_n+a_n^2)\\
		&= 2b_n^2-a^2_n\\
		&= -1(a^2_n-2b_n^2).
	\end{align*}
	We know from our induction hypothesis that $a_n^2-2b_n^2 = (-1)^n$, so
	\begin{align*}
		a_{n+1}^2-2b_{n+1}^2 &= -1(-1)^n \\
		a_{n+1}^2-2b_{n+1}^2 &= (-1)^{n+1}.
	\end{align*}
	Therefore, the equation holds for $n+1$, if it holds for a natural number $n$. By induction on $n$, the equation holds for all natural number $n$.

	So, it follows that  $(a_n)_{n\in\NN}$, $(b_n)_{n\in\NN}$ satisfy both 
	$$
	\left(1+\sqrt{2}\right)^n = a_n + b_n \sqrt{2} \qquad\mbox{and}\qquad a_n^2-2b_n^2 = (-1)^n,
	$$
	for all $n\in\NN$.
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{proof}
